---
title: "DDP - Wk2 - PA 1"
author: "b m g"
date: "6/11/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Assignment : Map Example using leaflet in R. Population levels 2015 for the top 20 cities and towns in Germany.

## Setting up libraries

```{r}
library(readr)
library(leaflet)
```
## Reading in Data

The German population data for 2015 can be found here
https://www.destatis.de/DE/ZahlenFakten/LaenderRegionen/Regionales/Gemeindeverzeichnis/Administrativ/Aktuell/05Staedte.html

Latitude and longtitude data for the top 20 towns and cities can be found here http://www.tageo.com/index-e-gm-cities-DE.htm

The URL data was gathered manually from Wikipedia and entered into the csv file. The csv file is locaated in the Data directory in the working directory.

```{r data}
pop_data <- read.csv("./Data/DE_Pop_2015.csv", header=TRUE, sep=";")
View(pop_data)
```

## Project the data onto a leaflet generated Map

The data is projected onto a leaflet generated map where marker diameter is currently not proportional to population. Marker diameter is scalled by dividing the square root of the population by 1,000 (one thousand).

The popups show the city name, population and URL for further information. The URL is not active at this time.

```{r}
mymap <- pop_data %>% 
                  leaflet() %>% 
                  addTiles() %>% 
                  addProviderTiles(providers$OpenStreetMap) %>% # added as per Forum week 2
                  addCircleMarkers(
                        lat=pop_data$Lat, lng=pop_data$Long, weight=5,
                        #radius=as.numeric(as.character(pop_data$Pop)),
                        popup = paste(as.character(pop_data$Name), 
                        "<BR>Population: ", pop_data$Pop, 
                        "<BR>", as.character(pop_data$URL)),
                  clusterOptions = markerClusterOptions()
                                    )
                  
mymap # plot the map to the viewer and knitr output file
```

## Aknowledgements

1. German census infomation from official government site https://www.destatis.de/DE/ZahlenFakten/LaenderRegionen/Regionales/Gemeindeverzeichnis/Administrativ/Aktuell/05Staedte.html

2. The population data was taken from following site http://www.tageo.com/index-e-gm-cities-DE.htm
